A data-intensive assessment of the species-abundance distribution.

### 2015-04-06 defense_pres.tex
Adds accessibility statement generator.
Adds a couple more pictures.

\documentclass[14pt]{beamer}
\usetheme{Pittsburgh}
\usepackage{xcolor}
\definecolor{USUBlue}{RGB}{26,57,89}
\usecolortheme[named=USUBlue]{structure}
\setbeamercolor{normal text}{fg=USUBlue}
\usepackage[utf8]{inputenc}
\usepackage{mathptmx}
\usepackage{tgbonum}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{marvosym}
\usefonttheme{structuresmallcapsserif}
\usefonttheme{serif}
\setbeamercolor{author}{fg=USUBlue}
\setbeamerfont{author}{size=\small}
\setbeamerfont{frametitle}{size=\large}
\setbeamertemplate{enumerate items}[default]
\author{Elita Baldridge\\ @elitabaldridge}
\title[17pt]{A data-intensive assessment of the species-abundance distribution.}
\setbeamertemplate{navigation symbols}{}
\date{}
%\setbeamercovered{transparent} 
%\logo{\includegraphics[scale=.03]{../Miscellaneous/Pictures/ecology_center_horizontal.jpg}\includegraphics[scale=0.07]{../Miscellaneous/Pictures/Weecology.png}} 
\institute{\includegraphics[scale=.07]{../Miscellaneous/Pictures/ecology_center_horizontal.jpg}\includegraphics[scale=0.35]{./sad-data/dissertation/WeecologyProduction.png}} 
%\subject{} 
\begin{document}
\section{Usage Notes}
\begin{frame}[t]
\begin{huge}
Feel free to:\\
\end{huge}
\includegraphics[scale=.5]{./sad-data/dissertation/use.png}\\
\begin{huge}
Provided that:\\
\end{huge}
\includegraphics[scale=.5]{./sad-data/dissertation/attribution.png}
\end{frame}

@@

\section{Introduction}
\subsection{What is macroecology?}
\begin{frame}[t]
\frametitle{Macroecology}
\normalsize One approach for identifying general ecological patterns \& processes.
\begin{center}
\includegraphics[scale=.30]{./sad-data/dissertation/SpatialTaxonomic.png}
\end{center}
\note{
\begin{itemize}
\item Data intensive.
\item Large scales.
\end{itemize}
\begin{itemize}
\item Spatial
\item Temporal
\item Taxonomic
\end{itemize}
\begin{itemize}
\item Search for general patterns \& processes.
\end{itemize}}
\end{frame}

\subsection{Let's begin with an example..}
\begin{frame}
\frametitle{Let's begin with an example...}
\note{
Few common species.
Many rare species.
One of the most fundamental and ubiquitous patterns in ecology.}
Species abundance distribution (SAD)
\begin{itemize}
\item Describes the distribution of commonness \& rarity of species.
\end{itemize}
\begin{center}
\includegraphics[scale=.4]{./sad-data/dissertation/generichollowcurves.png}\\
\end{center}
\note{
\begin{itemize}
\item Many potential pattern-generating mechanisms.
\item Exhibits a hollow curve distribution.
\end{itemize}
Relative abundance distribution (RAD)
Species abundance distribution (SAD)}
\end{frame}

@@

@@

\begin{frame}[t]{}
\frametitle{Building a database}
\begin{itemize}
\item Decide on inclusion criteria.
\item Decide what variables to collect.
\item Decide on handling of missing data.
\item Decide on database structure.
\item Search for data.
\item Sort papers into useable and not.
\item Collect data.
\end{itemize}
\begin{center}
Record decisions at all steps:\\
~\\
\begin{large}
\emph{Metadata are important.}
\end{large}
\end{center}
\end{frame}

@@

\subsection{Data & Analysis}
\subsubsection{Model selection}
\begin{frame}[shrink=10]
\frametitle{SAD Comparisons}
~\\
~\\
Selected five models from four classes for comparison.
\begin{table}
\begin{tabular}{l|l}
 Model class & Form of the distribution\\ 
\hline
 Purely statistical & Logseries, Poisson lognormal\\
 Branching process & Zipf \\
 Population dynamics & Negative binomial\\
 Niche partitioning & Geometric \\
\end{tabular}
~\\
~\\
~\\
~\\
\caption{After B.J. McGill et al. 2007.}
\end{table}
\end{frame}

@@

\subsection{Data & Analysis}
\begin{frame}
\frametitle{Neutral Analysis}
Used the same data and model fitting approach.\\
Compared a non-neutral model (Poisson lognormal) to a neutral model (negative binomial).\\
\end{frame}

@@

\subsection{Accessibility}
\begin{frame}[t]{}
\frametitle{Accessibility}
\begin{center}
This dissertation brought to you by:
\end{center}
\begin{Large}
Disability accommodations\\
\end{Large}
~\\
\begin{itemize}
\item Remote access \& participation.\\
\item Accessibility information
\note{
\item Computational tools \& tricks.
\begin{itemize}
\item Version control (GitHub).
\item Publicly available data.
\item Programming skills (data manipulation \& analysis).
\end{itemize}}
\end{itemize}
\end{frame}

>>>>

\documentclass[14pt]{beamer}
\usetheme{Pittsburgh}
\usepackage{xcolor}
\definecolor{USUBlue}{RGB}{26,57,89}
\usecolortheme[named=USUBlue]{structure}
\setbeamercolor{normal text}{fg=USUBlue}
\usepackage[utf8]{inputenc}
\usepackage{mathptmx}
\usepackage{tgbonum}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{marvosym}
\usefonttheme{structuresmallcapsserif}
\usefonttheme{serif}
\setbeamercolor{author}{fg=USUBlue}
\setbeamerfont{author}{size=\small}
\setbeamerfont{frametitle}{size=\large}
\setbeamertemplate{enumerate items}[default]
\author{Elita Baldridge\\ @elitabaldridge}
\title[17pt]{A data-intensive assessment of the species-abundance distribution.}
\setbeamertemplate{navigation symbols}{}
\date{}
%\setbeamercovered{transparent} 
%\logo{\includegraphics[scale=.03]{../Miscellaneous/Pictures/ecology_center_horizontal.jpg}\includegraphics[scale=0.07]{../Miscellaneous/Pictures/Weecology.png}} 
\institute{\includegraphics[scale=.07]{../Miscellaneous/Pictures/ecology_center_horizontal.jpg}\includegraphics[scale=0.35]{./sad-data/dissertation/WeecologyProduction.png}} 
%\subject{}

\begin{document}

\section{Usage Notes}
\begin{frame}[t]
\frametitle{A data-intensive assessment of the species-abundance distribution.}
\begin{large}
Feel free to:\\
\end{large}
\includegraphics[scale=.5]{./sad-data/dissertation/use.png}\\
\begin{large}
Provided that:\\
\end{large}
\includegraphics[scale=.5]{./sad-data/dissertation/attribution.png}
\end{frame}

@@

\section{Introduction}
\subsection{Let's begin with an example..}
\begin{frame}
\frametitle{Let's begin with an example...}
\note{
Few common species.
Many rare species.
One of the most fundamental and ubiquitous patterns in ecology.}
Species abundance distribution (SAD)
\begin{itemize}
\item Describes the distribution of commonness \& rarity of species.
\end{itemize}
\begin{center}
\includegraphics[scale=.4]{./sad-data/dissertation/generichollowcurves.png}\\
\end{center}
\note{
\begin{itemize}
\item Many potential pattern-generating mechanisms.
\item Exhibits a hollow curve distribution.
\end{itemize}
Relative abundance distribution (RAD)
Species abundance distribution (SAD)}
\end{frame}

@@

\subsection{What is macroecology?}
\begin{frame}[t]
\frametitle{Macroecology}
\normalsize One approach for identifying general ecological patterns \& processes.
\begin{center}
\includegraphics[scale=.30]{./sad-data/dissertation/SpatialTaxonomic.png}
\end{center}
\note{
\begin{itemize}
\item Data intensive.
\item Large scales.
\end{itemize}
\begin{itemize}
\item Spatial
\item Temporal
\item Taxonomic
\end{itemize}
\begin{itemize}
\item Search for general patterns \& processes.
\end{itemize}}
\end{frame}

@@

\begin{frame}[t]{}
\frametitle{Building a database}
\note{
\begin{itemize}
\item Decide on inclusion criteria.
\item Decide what variables to collect.
\item Decide on handling of missing data.
\item Decide on database structure.
\item Search for data.
\item Sort papers into useable and not.
\item Collect data.
\end{itemize}}
\begin{center}
Record decisions at all steps:\\
~\\
\begin{large}
\emph{Metadata are important.}
\end{large}
\end{center}
\end{frame}

@@

\subsection{Data & Analysis}
\begin{frame}
\frametitle{SAD Comparisons}
\begin{center}
\includegraphics[scale=.35]{./sad-data/dissertation/SpatialTaxonomic.png}
\end{center}
\end{frame}

\subsubsection{Model selection}
\begin{frame}[shrink=10]
\frametitle{SAD Comparisons}
~\\
~\\
Selected five models from four classes for comparison.
\begin{table}
\begin{tabular}{l|l}
 Model class & Form of the distribution\\ 
\hline
 Purely statistical & Logseries, Poisson lognormal\\
 Branching process & Zipf \\
 Population dynamics & Negative binomial\\
 Niche partitioning & Geometric \\
\end{tabular}
~\\
~\\
~\\
~\\
\caption{After B.J. McGill et al. 2007.}
\end{table}
\end{frame}

@@

\subsection{Data & Analysis}
\begin{frame}
\frametitle{Neutral Analysis}
\frametitle{SAD Comparisons}
\begin{center}
\includegraphics[scale=.2]{./sad-data/dissertation/SpatialTaxonomic.png}
\end{center}
Used the same data and model fitting approach.\\
Compared a non-neutral model (Poisson lognormal) to a neutral model (negative binomial).\\
\end{frame}

@@

\subsection{Accessibility}
\begin{frame}[t]{}
\frametitle{This dissertation brought to you by:}
\begin{large}
Disability accommodations\\
\end{large}
Accessibility statement generator
\begin{center}
\includegraphics[scale=.4]{./sad-data/dissertation/trinket-access-generator.png}\\
https://trinket.io/python/2df3ea45cf
\end{center}
\note{
\begin{itemize}
\item Computational tools \& tricks.
\begin{itemize}
\item Version control (GitHub).
\item Publicly available data.
\item Programming skills (data manipulation \& analysis).
\end{itemize}}
\end{frame}
